\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{fullpage}
\usepackage{hyperref}

\usepackage{titling}
\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\large#1\end{center}
    \vskip0.5em}%
}

\author{Michele Carignani, Alessandro Lenzi}
\title{Community discovery in Milan}
\subtitle{project for the course of Distributed Enabling Platforms}

\makeindex

\begin{document}

\maketitle
\tableofcontents

\begin{abstract}
The aim of the project is to analyze and then visualize telecommunication data
in order to discover real-world communities basing on the strength of connection
between different geographical areas. We implemented a pipeline of
map reduce job with the Hadoop distributed computation
environment\footnote{http://hadoop.apache.org/}.
In \ref{thedataset} and \ref{ds_analysis} of this report, we describe the original dataset
and analyze its properties. Then in \ref{aggregation}
we explain how we rearranged the data in
order to reduce the noise and improve the tractability and robustness of the
community discovery phase. Sections \ref{approaches}, \ref{mcl} will then
briefly describe two different approaches for community discovery
(finding strongly connected components and markovian clustering)
and in detail describe strategy and implementation of the latter which has
proved to give more significant results.
Finally \ref{results} will collect results and conclusion of the developed project.
\end{abstract}

%% Dataset and analysis
\input{Dataset.tex}

%% How aggregated graphs are generated
\input{Aggregation.tex}


\section{Communities discovery approaches}
\label{approaches}

Once the aggregated graph is produced (as list of weighted edges) is time to compute
the communities (i.e. the clusters) over it.

Two different approaches were developed and tested. 
As we will see, the second will give the
expected results, while the first will fail.

\subsection{Tarjan Connected Components algorithm}

Defining the communities as connected components onto the graph\footnote{A connected component
in a graph $A = (N,E)$ is a subset of nodes $A' \in A$  s.t. each node in A' is connected to 
all the other nodes in A' 
%% todo: more formal definition?
}, the first idea was to apply Tarjan's algorithm for connected components.
%% todo: reference

The algorithm can be described briefly as follows:
\begin{verbatim}
findConnectedComponents(node):
  for n in node.forward_star():
     
intial_node = get_initial_node()
\end{verbatim}

After testing Tarjan's algorithm it was evident that the order of the visit
was affecting the results of the application	.

The different strategies in choosing the starting node and ordering its forward
star showed different components.

So the next step was to introduce randomization in this choices.

A new problem then showed up: since the graph was extremely connected, the result
was a unique huge component.

To try to tackle this issue, we tried to define a treshold over edges weights, discarding all
edges with weight under the treshold.

This strategy improved the results in terms of number and size of the connected components
(respectively increased and decreased) but still introducing a "hard coded" treshold (even if
after analysing the distribution of arcs) was a too strong bias in the research.

The conclusion to be made was that the global approach of searching communities through visists
of the graph was misleading and prone to noise.

\subsection{Markov Clustering}

We then looked at a diffferent approach: Markov Clustering based on the Markov Clustering Algotirthm by Stijn van Dongen\footnote{\url{http://micans.org/mcl/}}.

The idea was to reduce noise and emphasize relations in a more structured way
by multiplying the adjancy matrix of the graph by itself until the number of
non-null elements in each row is very low (reduce the number of edges) and with
values probability weight close to 1 (taking the most probable connections).

File: MarkovClustering.java

\input{MarkovClustering.tex}

\section{Risultati}
\label{results}

\end{document}
